Theory about Normal Basis on $F(2^k)$

### 2016-12-24 dissertation/submission/prelim_GF.tex
dissertation after defense update 2

Fields of the form $\F_{p^{k}}$ are called Galois extension fields.
We are specifically interested in extension fields of type 
$\Fkk$, where $k > 1$. These are extensions of the binary
field $\F_2$.
\begin{Example}
Addition and multiplication operations over $\F_2$:
\begin{table}[!h]
	\centering
	\begin{tabular}{m{1cm}|l|ll|m{1cm}}
	\hhline{~---~}
	\multirow{3}{*}{} & $+$ & $0$ & $1$ & \multirow{3}{*}{} \\
	\hhline{~---~}
	& $0$ & $0$ & $1$ & \\
	& $1$ & $1$ & $0$ & \\
	\hhline{~---~}
	\multicolumn{5}{c}{}\\
	\multicolumn{5}{c}{Addition over $\F_2$}\\
	\end{tabular}
	\quad
	\begin{tabular}{m{1cm}|l|ll|m{1cm}}
	\hhline{~---~}
	\multirow{3}{*}{} & $\cdot$ & $0$ & $1$ & \multirow{3}{*}{} \\
	\hhline{~---~}
	& $0$ & $0$ & $0$ & \\
	& $1$ & $0$ & $1$ & \\
	\hhline{~---~}
	\multicolumn{5}{c}{}\\
	\multicolumn{5}{c}{Multiplication over $\F_2$}\\
	\end{tabular}
\end{table}

Notice that addition over $\F_2$ is a Boolean {\sc XOR} operation, 
because it is performed modulo $2$.
Similarly, multiplication over $\F_2$ performs a Boolean {\sc AND} operation.
\end{Example}

@@

\begin{table}[h]
\begin{center}
\caption{Bit-vector, Exponential and Polynomial representation of
elements in  $\mathbb{F}_{2^4} = \mathbb{F}_2[x] \pmod{x^4+x^3+1}$}\label{tab:gfelement} 
\begin{tabular}{|c|c|c||c|c|c|} 
\hline
$a_3a_2a_1a_0$ & Exponential & Polynomial     &$a_3a_2a_1a_0$ & Exponential & Polynomial  \\
\hline
$0000$        & $0$         & $0$            & $1000$ & $\alpha^3$ &  $\alpha^3$\\
\hline
$0001$        & $1$         & $1$            & $1001$ & $\alpha^4$ & $\alpha^3 + 1$\\
\hline
$0010$        & $\alpha$    & $\alpha$       & $1010$ & $\alpha^{10}$&$\alpha^3 + \alpha$  \\
\hline
$0011$        & $\alpha^{12}$& $\alpha + 1$   & $1011$ & $\alpha^5$ & $\alpha^3+\alpha+1$\\
\hline
$0100$        & $\alpha^2$  & $\alpha^2$     &  $1100$ & $\alpha^{14}$ & $\alpha^3 + \alpha^2$\\
\hline
$0101$        & $\alpha^9$   &$\alpha^2 + 1$ & $1101$  &$\alpha^{11}$  & $\alpha^3+\alpha^2+1$\\
\hline
$0110$        & $\alpha^{13}$& $\alpha^2 + \alpha$ & $1110$ & $\alpha^8$& $\alpha^3+\alpha^2+\alpha$\\
\hline
$0111$        &$\alpha^7 $ & $\alpha^2+\alpha+1$ & $1111$ &$\alpha^6$ & $\alpha^3+\alpha^2+\alpha+1$\\
\hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/MasseyOmura.pdf}
\caption{A typical SMSO structure of Massey-Omura multiplier}
\label{fig:MasseyOmura}}
\end{figure}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/mySMPO.eps}
\caption{5-bit Agnew's SMPO. Index $i$ satisfies $0<i<4$, indices $u,v$ are determined by column \# of nonzero entries in $i$-th row of $\lambda$-Matrix $M^{(0)}$, {\it i.e.} if entry $M_{ij}^{(0)}$ is a nonzero entry, $u$ or $v$ equals to $i+j \pmod 5$. Index $w = 2i\pmod 5$}
\label{fig:SMPO}}
\end{figure}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/5bitRH.pdf}
\caption{5-bit RH-SMPO}
\label{fig:5bitRH}}
\end{figure}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=3in]{newfig/multitable.pdf}
\caption{A $5\times 5$ multiplication table}
\label{fig:multitable}}
\end{figure}

>>>>

Fields of the form $\F_{p^{k}}$ are called Galois extension fields.
We are specifically interested in extension fields of type 
$\Fkk$, where $k > 1$. These are extensions of the binary
field $\F_2$.

\begin{table}[!h]
\caption{Addition and multiplication operations over $\F_2$.}
	\centering
	\begin{tabular}{m{1cm}|l|ll|m{1cm}}
	\hhline{~---~}
	\multirow{3}{*}{} & $+$ & $0$ & $1$ & \multirow{3}{*}{} \\
	\hhline{~---~}
	& $0$ & $0$ & $1$ & \\
	& $1$ & $1$ & $0$ & \\
	\hhline{~---~}
	\multicolumn{5}{c}{}\\
	\multicolumn{5}{c}{Addition over $\F_2$}\\
	\end{tabular}
	\quad
	\begin{tabular}{m{1cm}|l|ll|m{1cm}}
	\hhline{~---~}
	\multirow{3}{*}{} & $\cdot$ & $0$ & $1$ & \multirow{3}{*}{} \\
	\hhline{~---~}
	& $0$ & $0$ & $0$ & \\
	& $1$ & $0$ & $1$ & \\
	\hhline{~---~}
	\multicolumn{5}{c}{}\\
	\multicolumn{5}{c}{Multiplication over $\F_2$}\\
	\end{tabular}
\end{table}

Notice that addition over $\F_2$ is a Boolean {\sc XOR} operation, 
because it is performed modulo $2$.
Similarly, multiplication over $\F_2$ performs a Boolean {\sc AND} operation.

@@

\begin{table}[h]
\begin{center}
\caption{Bit-vector, Exponential and Polynomial representation of
elements in  $\mathbb{F}_{2^4} = \mathbb{F}_2[x] \pmod{x^4+x^3+1}$.}\label{tab:gfelement} 
\begin{tabular}{|c|c|c||c|c|c|} 
\hline
$a_3a_2a_1a_0$ & Exponential & Polynomial     &$a_3a_2a_1a_0$ & Exponential & Polynomial  \\
\hline
$0000$        & $0$         & $0$            & $1000$ & $\alpha^3$ &  $\alpha^3$\\
\hline
$0001$        & $1$         & $1$            & $1001$ & $\alpha^4$ & $\alpha^3 + 1$\\
\hline
$0010$        & $\alpha$    & $\alpha$       & $1010$ & $\alpha^{10}$&$\alpha^3 + \alpha$  \\
\hline
$0011$        & $\alpha^{12}$& $\alpha + 1$   & $1011$ & $\alpha^5$ & $\alpha^3+\alpha+1$\\
\hline
$0100$        & $\alpha^2$  & $\alpha^2$     &  $1100$ & $\alpha^{14}$ & $\alpha^3 + \alpha^2$\\
\hline
$0101$        & $\alpha^9$   &$\alpha^2 + 1$ & $1101$  &$\alpha^{11}$  & $\alpha^3+\alpha^2+1$\\
\hline
$0110$        & $\alpha^{13}$& $\alpha^2 + \alpha$ & $1110$ & $\alpha^8$& $\alpha^3+\alpha^2+\alpha$\\
\hline
$0111$        &$\alpha^7 $ & $\alpha^2+\alpha+1$ & $1111$ &$\alpha^6$ & $\alpha^3+\alpha^2+\alpha+1$\\
\hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/MasseyOmura.pdf}
\caption{A typical SMSO structure of Massey-Omura multiplier.}
\label{fig:MasseyOmura}}
\end{figure}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/mySMPO.eps}
\caption{5-bit Agnew's SMPO. Index $i$ satisfies $0<i<4$, indices $u,v$ are determined by column \# of nonzero entries in $i$-th row of $\lambda$-Matrix $M^{(0)}$, {\it i.e.} if entry $M_{ij}^{(0)}$ is a nonzero entry, $u$ or $v$ equals to $i+j \pmod 5$. Index $w = 2i\pmod 5$.}
\label{fig:SMPO}}
\end{figure}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/5bitRH.pdf}
\caption{A 5-bit RH-SMPO.}
\label{fig:5bitRH}}
\end{figure}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=3in]{newfig/multitable.pdf}
\caption{A $5\times 5$ multiplication table.}
\label{fig:multitable}}
\end{figure}

### 2016-12-24 dissertation/submission/prev.tex
dissertation after defense update 2

\begin{figure}[h]
\centerline{
\includegraphics[width=\textwidth]{newfig/unroll.pdf}
}
\caption{The unrolling of a sequential circuit}
\label{fig:unrolling}
\end{figure}

@@

\begin{figure}[h]
\centerline{
\includegraphics[width=0.45\textwidth]{newfig/BDD.pdf}
}
\caption{ROBDD representing Boolean function $\neg a \land b \land (c\lor d)$ with order $a>b>c>d$}
\label{fig:BDD}
\end{figure}

@@

Abstraction is a technique to reduce the state space representation by combining states with similar 
characteristics. Sometimes it can effectively lower the number of states that require analysis by orders of magnitude,
without affecting the properties we need to verify. Model checkers then utilize abstracted models 
with interpolation \cite{mcmillan2003interpolation,mcmillan:cav06}.
At first, abstraction was done manually by designers. Clarke {\it et al.} \cite{clarke2000counterexample}
proposed a BDD-based automated abstraction by removing spurious paths from analysis of counterexamples. 
Zhang {\it et al.} \cite{zhang2005design} proposed another abstraction method based on CNF-SAT.
It implemented latch abstraction by removing "irrelevant" latches by analyzing the 
UNSAT core from the $k$-BMC. Jain {\it et al.} \cite{HimanshuDAC2005} improved the abstraction refinement technique of \cite{clarke2000counterexample},
where they use CNF-SAT to perform the refinement instead of using BDDs. The new approach is applied to verify RTL Verilog
and was known to be successful.

>>>>

\begin{figure}[h]
\centerline{
\includegraphics[width=\textwidth]{newfig/unroll.pdf}
}
\caption{The unrolling of a sequential circuit.}
\label{fig:unrolling}
\end{figure}

@@

\begin{figure}[h]
\centerline{
\includegraphics[width=0.45\textwidth]{newfig/BDD.pdf}
}
\caption{ROBDD representing Boolean function $\neg a \land b \land (c\lor d)$ with order $a>b>c>d$.}
\label{fig:BDD}
\end{figure}

@@

Abstraction is a technique to reduce the state space representation by combining states with similar 
characteristics. Sometimes it can effectively lower the number of states that require analysis by orders of magnitude,
without affecting the properties we need to verify. Model checkers then utilize abstracted models 
with interpolation \cite{mcmillan2003interpolation,mcmillan:cav06}.
At first, abstraction was done manually by designers. Clarke {\it et al.} \cite{clarke2000counterexample}
proposed a BDD-based automated abstraction by removing spurious paths from analysis of counterexamples. 
Zhang {\it et al.} \cite{zhang2005design} proposed another abstraction method based on CNF-SAT.
It implemented latch abstraction by removing "irrelevant" latches by analyzing the 
UNSAT core from the $k$-BMC. Jain {\it et al.} \cite{jain2005word} improved the abstraction refinement technique of \cite{clarke2000counterexample},
where they use CNF-SAT to perform the refinement instead of using BDDs. The new approach is applied to verify RTL Verilog
and was known to be successful.

### 2016-12-24 dissertation/submission/recha.tex
dissertation after defense update 2

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/MIPS.pdf}
\caption{A 64-bit sequential multiplication hardware design}
\label{fig:MIPS}}
\end{figure}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=4in]{newfig/Lagrange.pdf}
\caption{Gate-level netlist for Lagrange's interpolation example}
\label{fig:Lagrange}}
\end{figure}

@@

For each element in $\F_{2^3}$, we write down the truth table as follows:
\begin{table}[H]
\label{tab:truthtable}
\centering{\small
\begin{tabular}{|c|ccc|c|}
\hline
$\{a_2a_1a_0\}\in\mathbb{B}^3$   & $A\in \F_{2^3}$ &$\rightarrow$& $\{z_2z_1z_0\}\in\mathbb{B}^3$  & $Z\in \F_{2^3}$ \\
\hline
000  &0 &$\rightarrow$&000 & 0 \\
001  &1 &$\rightarrow$&001 & 1 \\
010  &$\alpha$ & $\rightarrow$ & 111& $\alpha^2 + \alpha + 1$ \\
011  &$\alpha + 1$ &$\rightarrow$& 111 & $\alpha^2 + \alpha + 1$ \\
100  &$\alpha^2$ &$\rightarrow$& 101 &  $\alpha^2+1$ \\
101  &$\alpha^2 + 1$ &$\rightarrow$&011 & $\alpha+1$ \\
110  &$\alpha^2 + \alpha$&$\rightarrow$& 101 &$\alpha^2 + 1$ \\
111  &$\alpha^2 + \alpha + 1$ &$\rightarrow$& 101 &$\alpha^2 + 1$\\
\hline
\end {tabular}
}
\caption{Truth table for mappings in $\mathbb{B}^3$ and $\F_{2^3}$}
\end{table}
Now our objective is to abstract a function over finite field $\F_{2^3}$ in word-level variables, {\it i.e.} 
$Z = \Func(A)$. Recall Lagrange's interpolation formula:
\begin{equation}
\label{eqn:Lagrange}
\Func(x) =  \sum_{k=1}^N \left[ \prod_{(0\leq j \leq k-1),(j\neq i)}\frac{x-x_j}{x_i-x_j} \cdot y_k \right]
\end{equation}
The geometric meaning of Lagrange's interpolation in real algebra is: given $N$ points with coordinates $(x_i,y_i)$,
they can always be fitted into a polynomial function with at most $N-1$ degree, and that function can be 
written in the form of Equation \ref{eqn:Lagrange}. In this example, although defined in a Galois field instead of 
the real number field, the essential concept of Lagrange's interpolation remains the same. 
We can get 8 points in the affine space:
\begin{align*}
\text{Generic form}&: (a_2\alpha^2+a_1\alpha+a_0,z_2\alpha^2+z_1\alpha+z_0) \gets (A,Z) \\
\text{Point }1&: (0, 0) \gets (000,000) \\
\text{Point }2&: (1,1) \gets (001,001) \\
\text{Point }3&:  (\alpha,\alpha^2 + \alpha + 1) \gets (010,111)\\
\text{Point }4&:  (\alpha + 1,\alpha^2 + \alpha + 1)\gets (011,111) \\
\text{Point }5&:  (\alpha^2,\alpha^2+1) \gets (100,101)\\
\text{Point }6&:  (\alpha^2 + 1,\alpha+1)\gets (101,011)\\
\text{Point }7&:  (\alpha^2 + \alpha,\alpha^2 + 1)\gets (110,101)\\
\text{Point }8&:  (\alpha^2 + \alpha + 1,\alpha^2 + 1)\gets (111,101)
\end{align*}
Substitute 8 $(x_i,y_i)$ pairs in Equation \ref{eqn:Lagrange} with these 8 points in $\F_{2^3}$.
The result is a polynomial function with degree no greater than 7:
\begin{align*}
Z =& \Func(A) \\
=& (\alpha^2+\alpha+1) A^7 + (\alpha^2+1) A^6 + \alpha A^5 + (\alpha+1) A^4 \\
&+ (\alpha^2+\alpha+1)A^3+ (\alpha^2+1)A
\end{align*}

@@

\subsection{FSM Model for Sequential Circuits}
A finite state machine (FSM) is a mathematical model of computation for designing and analyzing sequential logic 
circuits. If a FSM's primary outputs depend on primary inputs and present state inputs, it is named as a \textit{Mealy machine};
the formal definition is as follows:
\begin{Definition}
A Mealy machine is an $n$-tuple $\mathcal M = (\Sigma,O,S,S^0,\Delta,\Lambda)$ where
\begin{itemize}
\item $\Sigma$ is the input label, $O$ is the output label;
\item $S$ is the set of states, $S^0\subseteq S$ is the set of initial states;
\item $\Delta:\ S\times\Sigma\to S$ is the next state transition function;
\item $\Lambda:\ S\times\Sigma\to O$ is the output function.
\end{itemize}
\end{Definition}
The other kind of FSM is \textit{Moore machine}, its difference from Mealy machine is that
its primary outputs only depend on the present states, {\it i.e.} the output function is defined as
$$\Lambda:\ S \to O$$
Typical sequential circuits can be depicted as Figure \ref{fig:seqmodel}(a). Primary inputs
$x_1,\dots,x_m \in \Sigma$, and primary outputs $z_1,\dots,z_n\in O$. Signals $s_1,\dots,s_k$ 
are present state (PS) variables, $t_1,\dots,t_k$ are next state (NS) variables.
We can define 2 $k$-bit words denoting the PS/NS variables as there are $k$ flip-flops
in the datapath: $S = (s_1,\dots,s_k), ~T=(t_1,\dots,t_k)$. Transition function
at bit level are defined as $\Delta_i$: 
$$t_i = \Delta_i(s_1,\dots,s_k,x_1,\dots,x_m)$$
\begin{figure}[H]
\centering{
%\begin{minipage}{12cm}
\includegraphics[width=5.5in]{newfig/seqmodel.pdf}
% \vspace{-0.2in}
\caption{FSM models of sequential circuits}
%\end{minipage}
\label{fig:seqmodel}}
\end{figure}
In some cases, arithmetic computations are implemented as Moore machines where input operands
are loaded into register files $R$ and the FSM is executed for $k$ clock cycles.
We can simplify them to the model in Figure \ref{fig:seqmodel}(b).

@@

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/proj_reacha.pdf}
\caption{Projection of the variety of circuit description ideal}
\label{fig:proj_reacha}}
\end{figure}

@@

\begin{figure}[hbt]
\centering{
\includegraphics[width=\textwidth]{newfig/PI.pdf}
\caption{PI partition of a sequential circuit}
\label{fig:PI}}
\end{figure}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/flowchart.pdf}
\caption{Execution process of word-level FSM traversal tool}
\label{fig:flowchart}}
\end{figure}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/SING.pdf}
\caption{Singular script for executing bit-to-word substitution and traversal loop}
\label{fig:SING}}
\end{figure}

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/Recha_result.pdf}
\caption{The output given by our traversal tool}
\label{fig:Recha_result}}
\end{figure}

@@

\begin{table}[H]
\centering
\caption{Results of running benchmarks using our tool. 
\small{Parts I to III denote the time taken by polynomial divisions,
  bit-level to word-level abstraction and iterative reachability
  convergence checking part of our approach, respectively.}}
{\small 
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|}
\hline
\multirow{3}{*}{\centering Benchmark} 
& \multirow{3}{0.9cm}{\centering \# Gates} 
& \multirow{3}{1.1cm}{\centering \# Latches} 
& \multirow{3}{*}{\centering \# PIs}
 & \multirow{3}{0.9cm}{\centering \# States}
 & \multirow{3}{1.3cm}{\centering \# iterations}
 & \multicolumn{3}{c|}{\multirow{2}{2.0cm}{\centering Runtime (sec)}}
 & \multirow{3}{1.8cm}{\centering Runtime of VIS (sec)} \\
  & & & & & &\multicolumn{3}{c|}{}& \\
  \cline{7-9}
    & & & & & & I & II & III & \\
\hline
\hline
b01 & 39  & 5  & 2 & 18  & 5  & $<0.01$ & 0.01 & 0.02 & $<0.01$\\
b02 & 24  & 4  & 1 & 8 & 5 & $<0.01$  & 0.01 & $<0.01$ & $<0.01$ \\
b06 & 49  & 9  & 2 & 13 & 4 & $<0.01$ & 0.07 & 5.0 & $<0.01$ \\
s27 & 10 & 3 & 4 & 6 & 2 & $<0.01$ & 0.01 & 0.02  & $<0.01$  \\
s208 & 61 & 8 & 11 & 16 & 16 & $<0.01$ & 0.32 & 2.4 & $<0.01$ \\
s386 & 118 & 6 & 13 & 13  & 3 & 1.0 & 7.6 & 8.2  & $<0.01$ \\
bbara & 82 & 4 & 4 & 10 & 6 & 0.04 & 0.01 & 0.04  & $<0.01$ \\
beecount & 48  & 3  & 3 & 7  & 3  &$<0.01$ & 0.01 & 0.01 & $<0.01$ \\
dk14 & 120  & 3  & 3 & 7  & 2  & 45 & $<0.01$ & 0.08 & $<0.01$\\
donfile & 205  & 5  & 2 & 24 & 3  & 12316 & 0.02 & 1.7  & $<0.01$\\
\hline
\end{tabular}
}
\label{tab:recha_result}  
\end{table}

>>>>

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/MIPS.pdf}
\caption{A 64-bit sequential multiplication hardware design.}
\label{fig:MIPS}}
\end{figure}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=4in]{newfig/Lagrange.pdf}
\caption{Gate-level netlist for Lagrange's interpolation example.}
\label{fig:Lagrange}}
\end{figure}

@@

For each element in $\F_{2^3}$, we write down the truth table as follows:
\begin{table}[H]
\label{tab:truthtable}
\caption{Truth table for mappings in $\mathbb{B}^3$ and $\F_{2^3}$.}
\centering{\small
\begin{tabular}{|c|ccc|c|}
\hline
$\{a_2a_1a_0\}\in\mathbb{B}^3$   & $A\in \F_{2^3}$ &$\rightarrow$& $\{z_2z_1z_0\}\in\mathbb{B}^3$  & $Z\in \F_{2^3}$ \\
\hline
000  &0 &$\rightarrow$&000 & 0 \\
001  &1 &$\rightarrow$&001 & 1 \\
010  &$\alpha$ & $\rightarrow$ & 111& $\alpha^2 + \alpha + 1$ \\
011  &$\alpha + 1$ &$\rightarrow$& 111 & $\alpha^2 + \alpha + 1$ \\
100  &$\alpha^2$ &$\rightarrow$& 101 &  $\alpha^2+1$ \\
101  &$\alpha^2 + 1$ &$\rightarrow$&011 & $\alpha+1$ \\
110  &$\alpha^2 + \alpha$&$\rightarrow$& 101 &$\alpha^2 + 1$ \\
111  &$\alpha^2 + \alpha + 1$ &$\rightarrow$& 101 &$\alpha^2 + 1$\\
\hline
\end {tabular}
}
\end{table}
Now our objective is to abstract a function over finite field $\F_{2^3}$ in word-level variables, {\it i.e.} 
$Z = \Func(A)$. Recall Lagrange's interpolation formula:
\begin{equation}
\label{eqn:Lagrange}
\Func(x) =  \sum_{k=1}^N \left[ \prod_{(0\leq j \leq k-1),(j\neq i)}\frac{x-x_j}{x_i-x_j} \cdot y_k \right]
\end{equation}
The geometric meaning of Lagrange's interpolation in real algebra is: given $N$ points with coordinates $(x_i,y_i)$,
they can always be fitted into a polynomial function with at most $N-1$ degree, and that function can be 
written in the form of Equation \ref{eqn:Lagrange}. In this example, although defined in a Galois field instead of 
the real number field, the essential concept of Lagrange's interpolation remains the same. 
We can get 8 points in the affine space:
\begin{align*}
\text{Generic form}&: (a_2\alpha^2+a_1\alpha+a_0,z_2\alpha^2+z_1\alpha+z_0) \gets (A,Z) \\
\text{Point }1&: (0, 0) \gets (000,000) \\
\text{Point }2&: (1,1) \gets (001,001) \\
\text{Point }3&:  (\alpha,\alpha^2 + \alpha + 1) \gets (010,111)\\
\text{Point }4&:  (\alpha + 1,\alpha^2 + \alpha + 1)\gets (011,111) \\
\text{Point }5&:  (\alpha^2,\alpha^2+1) \gets (100,101)\\
\text{Point }6&:  (\alpha^2 + 1,\alpha+1)\gets (101,011)\\
\text{Point }7&:  (\alpha^2 + \alpha,\alpha^2 + 1)\gets (110,101)\\
\text{Point }8&:  (\alpha^2 + \alpha + 1,\alpha^2 + 1)\gets (111,101)
\end{align*}
Substitute 8 $(x_i,y_i)$ pairs in Equation \ref{eqn:Lagrange} with these 8 points in $\F_{2^3}$.
The result is a polynomial function with degree no greater than 7:
\begin{align*}
Z =& \Func(A) \\
=& (\alpha^2+\alpha+1) A^7 + (\alpha^2+1) A^6 + \alpha A^5 + (\alpha+1) A^4 \\
&+ (\alpha^2+\alpha+1)A^3+ (\alpha^2+1)A
\end{align*}

@@

\subsection{FSM Model for Sequential Circuits}
A finite state machine (FSM) is a mathematical model of computation for designing and analyzing sequential logic 
circuits. If a FSM's primary outputs depend on primary inputs and present state inputs, it is named as a \textit{Mealy machine};
the formal definition is as follows:
\begin{Definition}
A Mealy machine is an $n$-tuple $\mathcal M = (\Sigma,O,S,S^0,\Delta,\Lambda)$ where
\begin{itemize}
\item $\Sigma$ is the input label, $O$ is the output label;
\item $S$ is the set of states, $S^0\subseteq S$ is the set of initial states;
\item $\Delta:\ S\times\Sigma\to S$ is the next state transition function;
\item $\Lambda:\ S\times\Sigma\to O$ is the output function.
\end{itemize}
\end{Definition}
The other kind of FSM is \textit{Moore machine}, its difference from Mealy machine is that
its primary outputs only depend on the present states, {\it i.e.} the output function is defined as
$$\Lambda:\ S \to O$$
Typical sequential circuits can be depicted as Figure \ref{fig:seqmodel}(a). Primary inputs
$x_1,\dots,x_m \in \Sigma$, and primary outputs $z_1,\dots,z_n\in O$. Signals $s_1,\dots,s_k$ 
are present state (PS) variables, $t_1,\dots,t_k$ are next state (NS) variables.
We can define 2 $k$-bit words denoting the PS/NS variables as there are $k$ flip-flops
in the datapath: $S = (s_1,\dots,s_k), ~T=(t_1,\dots,t_k)$. Transition function
at bit level are defined as $\Delta_i$: 
$$t_i = \Delta_i(s_1,\dots,s_k,x_1,\dots,x_m)$$
\begin{figure}[H]
\centering{
%\begin{minipage}{12cm}
\includegraphics[width=5.5in]{newfig/seqmodel.pdf}
% \vspace{-0.2in}
\caption{FSM models of sequential circuits.}
%\end{minipage}
\label{fig:seqmodel}}
\end{figure}
In some cases, arithmetic computations are implemented as Moore machines where input operands
are loaded into register files $R$ and the FSM is executed for $k$ clock cycles.
We can simplify them to the model in Figure \ref{fig:seqmodel}(b).

@@

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/proj_reacha.pdf}
\caption{Projection of the variety of circuit description ideal.}
\label{fig:proj_reacha}}
\end{figure}

@@

\begin{figure}[hbt]
\centering{
\includegraphics[width=\textwidth]{newfig/PI.pdf}
\caption{PI partition of a sequential circuit.}
\label{fig:PI}}
\end{figure}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/flowchart.pdf}
\caption{Execution process of word-level FSM traversal tool.}
\label{fig:flowchart}}
\end{figure}

@@

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/SING.pdf}
\caption{Singular script for executing bit-to-word substitution and traversal loop.}
\label{fig:SING}}
\end{figure}

\begin{figure}[H]
\centering{
\includegraphics[width=\textwidth]{newfig/Recha_result.pdf}
\caption{The output given by our traversal tool.}
\label{fig:Recha_result}}
\end{figure}

@@

\begin{table}[H]
\centering
\caption{Results of running benchmarks using our tool. 
\small{Parts I to III denote the time taken by polynomial divisions,
  bit-level to word-level abstraction and iterative reachability
  convergence checking part of our approach, respectively.}}
{\small 
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|}
\hline
\multirow{3}{*}{\centering Benchmark} 
& \multirow{3}{0.9cm}{\centering \# Gates} 
& \multirow{3}{1.1cm}{\centering \# Latches} 
& \multirow{3}{*}{\centering \# PIs}
 & \multirow{3}{0.9cm}{\centering \# States}
 & \multirow{3}{1.2cm}{\centering \# iterations}
 & \multicolumn{3}{c|}{\multirow{2}{2.0cm}{\centering Runtime (sec)}}
 & \multirow{3}{1.3cm}{\centering Runtime of VIS (sec)} \\
  & & & & & &\multicolumn{3}{c|}{}& \\
  \cline{7-9}
    & & & & & & I & II & III & \\
\hline
\hline
b01 & 39  & 5  & 2 & 18  & 5  & $<0.01$ & 0.01 & 0.02 & $<0.01$\\
b02 & 24  & 4  & 1 & 8 & 5 & $<0.01$  & 0.01 & $<0.01$ & $<0.01$ \\
b06 & 49  & 9  & 2 & 13 & 4 & $<0.01$ & 0.07 & 5.0 & $<0.01$ \\
s27 & 10 & 3 & 4 & 6 & 2 & $<0.01$ & 0.01 & 0.02  & $<0.01$  \\
s208 & 61 & 8 & 11 & 16 & 16 & $<0.01$ & 0.32 & 2.4 & $<0.01$ \\
s386 & 118 & 6 & 13 & 13  & 3 & 1.0 & 7.6 & 8.2  & $<0.01$ \\
bbara & 82 & 4 & 4 & 10 & 6 & 0.04 & 0.01 & 0.04  & $<0.01$ \\
beecount & 48  & 3  & 3 & 7  & 3  &$<0.01$ & 0.01 & 0.01 & $<0.01$ \\
dk14 & 120  & 3  & 3 & 7  & 2  & 45 & $<0.01$ & 0.08 & $<0.01$\\
donfile & 205  & 5  & 2 & 24 & 3  & 12316 & 0.02 & 1.7  & $<0.01$\\
\hline
\end{tabular}
}
\label{tab:recha_result}  
\end{table}
